---
title: "A look at apprenticeship obtainment and the impact of economic factors on educationial otainment"
subtitle: "INFO 526 - Summer 2024 - Final Project"
author:
  - name: "Joshua Holmes"
    affiliations:
      - name: "School of Information, University of Arizona"
description: "Project description"
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
toc: true
editor: visual
code-annotations: hover
execute:
  warning: false
---

```{r}
#| label: load-pkgs
#| message: false
library(tidyverse)
library(here)

```

## Dataset

```{r}
#| label: load-dataset
#| message: false

english_education <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-01-23/english_education.csv')

#The dataset I plan on using is from the UK office of national statistics and has data about eductation attianment based for multiple towns and cites. We can see the dimensions of the the data below as well as the name of the columns by running the below code.

names(english_education)


```

A brief description of your dataset including its provenance, dimensions, etc. as well as the reason why you chose this dataset.

The data set contains columns related to towns, town codes, town names, population, regional information, coastal classification, job density, income, university presence, and education attainment statistics. The dataset contains 1104 rows and 31 columns.

Make sure to load the data and use inline code for some of this information.

## Questions

The two questions you want to answer.

For my first question will be to look at the the relationship between university presence and region on the number of 19-year-old in apprenticeships.

For my second question I want to see if there is a relationship between higher income and job density leads to higher education scores. This would suggest that economic factors play a significant role in educational attainment.

Analysis plan

-   For question one - I need to normalize the 19-year-old in Apprenticeships to population as we would expect that towns with a high population would have larger number of 19-year old. To normalize this I will sum all the activity at 19-years and then find the percentage of that number that are in apprenticeships. This will be our Y-axis. Our x-axis will be if their is a university present. Then I will have the regions set colors.

-   For question two - I will created a 3D scatter plot with the following variables. X-axis will be income, Y-axis will be job Density and the Z-axis will be Education score. I will also add color to the education score to add a heat map effect to clearing distinguish where we are seeing high educational scores.
